---
title: "p8105_hw5_ym2813"
author: "Anna Ma"
date: "11/18/2021"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
library(p8105.datasets)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1 

```{r, message=FALSE}
homicides_df = 
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved")
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

**Describe the data**

The dataset consists of `r nrow(homicides_df)` observations and `r ncol(homicides_df)` variables a tidying it up. Each row of the data is a reported homicide case, including record of the victim's name, race/ethnicity, age, sex, location of the crime, and whether the crime was solved. 

**Resolution of each City**

```{r}
homicides_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()) 
```


**Baltimore**
```{r}
baltimore_df = 
  homicides_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n())

balimtore_test = 
  prop.test(x = baltimore_summary %>% pull(unsolved), 
            n = baltimore_summary %>% pull(n))

balimtore_test %>% 
  broom::tidy()
```

**For all Cities**

Function

```{r}
prop_test_function = function(city_df) {
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(x = city_summary %>% pull(unsolved), 
            n = city_summary %>% pull(n))
  
  return(city_test)
}
```

Use the function and iterate across all cities
```{r}
results_df = 
  homicides_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

results_df
```

**Plot**
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r, include=FALSE}
## Another Method 
homicides_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test), 
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```


## Problem 2

**Tidy the Dataframe**
```{r, message=FALSE}
arm_df = 
  #dataframe containing all file names
  tibble(
    file_name = list.files("data/data_prob2/")) %>% 
  #Iterate over file names and read in data for each subject using map and saving the result as a new variable in the dataframe
  mutate(
    subject_data = map(str_c("data/data_prob2/",file_name), read_csv)) %>% 
  #unnest the data for each subject
  unnest(subject_data)

#tidy the dataset 
subject_df = 
  arm_df %>% 
    #manipulate file names to include control arm and subject ID
    separate(file_name, into = c("arm", "id"), sep = "_") %>% 
    #tidy the variable names
    mutate(
      id = str_replace(id,".csv","")
    ) %>% 
  #tidy data for each week
    pivot_longer(
      week_1:week_8,
      names_to = "week",
      names_prefix = "week_",
      values_to = "observation"
    ) %>% 
  #assign appropriate classes to the variables
  mutate(
    arm = recode(arm, con = "control", exp = "experimental"),
    arm = factor(arm),
    id = factor(id),
    week = as.integer(week)
  )

subject_df
```

**Spaghetti plot**

```{r}
subject_df %>% 
  ggplot(aes(x = week, y = observation, group = id, color = id)) +
  geom_point() +
  geom_line() +
  facet_grid(. ~ arm)
```

From the plots, we can observe that the observed data has no significant variation through the 8 weeks period for the control group. However, for the experimental group, there exists a positive trend for the observation value, indicating that there is a positive linear relationship. 
